---
title: "Methods"
author: "Kassandra Franco"
date: "5/28/2018"
output: html_document
---

#Survey Development and Design

```{r, message = FALSE, warning = FALSE, echo = FALSE}

tags$img (class = "sign", src = "survey-sign-1.jpg", width = 300)

```

Our survey starts out with the picture above, and asks survey takers what the first word that
comes to mind is upon seeing it. This is meant to gauge people's first reactions to the signs,
and to show this we created a word cloud. Two sections follow: Demographics and Resilience Lab Signs.

The demographics section is meant to gauge the demographics of our sample, and to determine the
possible need for weights. We ask about gender, ethnicy, age, year in school, major/intended major,
minor, own rating of mental health, experience regarding microaggressions and microcompassions
relative to peers, and whether or not they browse UW's main Facebook meme page: UW Teens for Boundless
Memes. This section ends by asking if the survey taker has seen the Resilience Lab signs, and
if they answer no, the survey closes as the rest of the questions are not applicable to these people.

The Resilience Lab Signs section is meant to further understand the survey taker's perceptions of, 
reactions to, and behavioral change from the signs. Here, we ask about where the people first saw 
the signs, whether or not they followed the website provided (resilience.uw.edu) on the signs, 
whether or not their feelings changed and how, how uplifted or discouraged they felt, if their 
behavior changed and how, if they've talked to others about the signs and what they talked about, and
finally, how they rate the effectiveness of the signs in terms of promoting microcompassions on campus.

Both sections are important as we used them to draw relationships among different factors within 
each of the sections (ethnicity versus mental health, rating of mental health versus exerpience with 
microaggressions, feelings of being uplifted versus rating of signs' effectiveness at promoting
microcompassions) but also among different factors between the two (major versus rating of signs' 
effectiveness at promoting microcompassions, rating of mental health versus feelings of being
uplifted).

# Population and Sample Demographics

The population of interest is the UW student community, as they are the main target of the 
Resilience Lab signs. In terms of keeping our sample representative of the UW student population,
we care most about two main demographical dimensions: ethnicity and major. The following tables show 
UW's makeup and theblah  #add

```{r, message = FALSE, warning = FALSE, echo = FALSE}

library(ggplot2)

ethnicities <- c("Caucasian", "Asian", "International", "Latino", "Two or more races", "Black/African", "Prefer not to answer/NA", "Hawaiian/Pacific Islander", "American Indian/Alaska Native")
uw.percentage <- c(40.3, 24.6, 14.6, 8.1, 7.4, 3.0, 1.1, 0.5, 0.4)
uw_ethnic_makeup <- data.frame(ethnicities, uw.percentage, stringsAsFactors = FALSE)

source("../prep-data.R")
survey_ethnic_makeup <- select(data, timestamp, ethnicity)
num_survey_takers <- nrow(survey_ethnic_makeup)

grouped_survey_ethnic_makeup <- 
  group_by(survey_ethnic_makeup, ethnicity) %>% 
  summarize(n = n()) %>% 
  mutate(survey.percentage = round(n*100/num_survey_takers), digits = 2) %>% 
  select(ethnicity, survey.percentage)

ethnicity_plot <- ggplot(uw_ethnic_makeup, aes(x = ethnicities, y = percentage)) +
  geom_bar(stat = "identity") +
  labs(title = "Ethnicity Breakdown UW Student Population vs. Survey Sample",
       x = "Ethnicity", y = "Percentage") 

```

# Limitations

The somethign something blah") #add

